\documentclass[a4paper, 10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[top=0.75in, bottom=1in, left=1.3in, right=1.3in]{geometry}
\usepackage{lipsum}
\usepackage{datetime}
\usepackage{ragged2e}

% Start of the document
\begin{document}

\small
% Sender's Address
\begin{flushright}
Finrod Felagund \\
Dorthonion, Beleriand, Middle Earth \\
felagund@nargothrond.xyz
\end{flushright}

% Date
\begin{flushright}
\today
\end{flushright}

% Receiver's Address
\begin{flushleft}
Elu Thingol - King of the Teleri \& Lord of Beleriand \\
Menegroth, The Thousand Caves, \\
Doriath, Beleriand, Middle Earth \\
thingol@menegroth.xyz
\end{flushleft}

% Body of the Letter
\begin{justify}
Dear King,
\\ \\
\indent The situation is grave. The forces of Morgoth have broken the siege of Angband, the Ard-galen has been scorched by flame, and our rear-lines on the Dorthonion highlands are nearing collapse. A new foe they are calling Glaurung has been released upon our lands. Nargothrond, our stronghold, stands resilient against this terror, but our strength is diminishing. We are in urgent need of reinforcements. Without additional warriors, archers, spies, and those skilled in war, our chances of withstanding this onslaught lessen with each passing day. 
\\ \\
\indent The Great Foe is spurred by bloodlust, and we fight for the survival of our people and land. Our fates are intertwined in this fight against the darkness. An assault on Nargothrond is an assault on all who stand against Morgoth. Send us your bravest and most courageous. Together, we have a chance to turn the tide, to fortify our defenses, and to protect our home.
\\ \\
\indent I await your prompt response. Victory is within our reach. 

\end{justify}

% Closing the Letter
\vspace{0.2in}
\hrule
\vspace{0.2in}
\begin{flushleft}
In starlight and in hope, Na lu e-govaded vín \\
Finrod Felagund
\end{flushleft}

\end{document}
