\documentclass[a4paper, 10pt]{article}
\pagestyle{empty}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[top=0.5in, bottom=0.5in, left=0.8in, right=0.8in]{geometry}
\usepackage{enumitem}
\usepackage{enumitem,ragged2e}

\newcommand{\header}[1]{
    \begin{center}
        {\Large \textbf{#1}}
    \end{center}
}

\newcommand{\sectiontitle}[1]{
    \vspace{8pt}
    \footnotesize
    \noindent{\large \textbf{#1}}
    \vspace{3pt}
    \hrule
    \vspace{6pt}
}

\newcommand{\entry}[4]{
    \vspace{6pt}
    \footnotesize
    \noindent
    \begin{tabular}{@{} p{0.2\linewidth} p{0.5\linewidth} p{0.25\linewidth} @{}}
        {#4} & \textbf{#1} -- \textbf{#2} & \hfill{#3} \\
    \end{tabular}
    \vspace{4pt}
}
\begin{document}

\header{Finrod Felagund}

\noindent
\vspace{-22pt} % Adjust the value to control the spacing between the name and contact information
\small
\begin{center}
Nargothrond, Beleriand, Middle Earth, felagund@nargothrond.xyz
\end{center}

\sectiontitle{Links}
\begin{itemize}[left=0.25\linewidth, noitemsep]
    \footnotesize
    \item \underline{\href{https://github.com/mattlianje}{nargothrond.xyz/workshop}},
    \underline{\href{https://nargothrond.xyz}{nargothrond.xyz/}}
\end{itemize}

\sectiontitle{Profile}
\begin{itemize}[left=0.25\linewidth, noitemsep]
    \footnotesize
    \item \textbf{Leadership:} Proven ability in establishing and ruling realms, leading forces in battle.
    \item \textbf{Diplomacy:} Exceptional skills in fostering relations with different races, particularly Men.
    \item \textbf{Loyalty:} Demonstrated courage and self-sacrifice in fulfilling oaths and protecting allies.
    \item \textbf{Architecture and Engineering:} Designing and building large-scale underground fortresses.
    \item \textbf{Combat:} Proficient in the use of Elven weapons, including longbows, and Elven blades.
\end{itemize}

\sectiontitle{Experience}

\entry{Born in Valinor, Journey to Middle-earth}{N/A}{Valinor, Aman}{Y.T. 1050 - Y.T. 1495}
\begin{itemize}[left=0.25\linewidth, noitemsep, before=\small]
    \footnotesize
    \item Eldest son of Finarfin and Eärwen.
    \item Departed for Middle-earth with my father and brothers after the theft of the Silmarils, gems created by my uncle Fëanor.
\end{itemize}


\entry{Captain, Soldier}{Battles of the Jewels}{Beleriand}{Y.T. 1495 - F.A. 60}
\begin{itemize}[left=0.25\linewidth, noitemsep, before=\small]
\footnotesize
    \footnotesize
    \item Participated in the early battles of Beleriand, demonstrating strategic acumen, and effective command of Elven forces. These battles include:
    \item \textbf{Dagor-nuin-Giliath (Battle-under-Stars)}: Engaged in high-intensity shock combat, and rapid manoeuvre warfare against Morgoth's diverse forces: Orcs, Trolls, and Balrogs.
    \item \textbf{The Dagor Aglareb (Glorious Battle)}: Faced Morgoth's renewed forces, demonstrated superior use of defense-in-depth, leading to a successful containment of the enemy advance. Employed a mix of rapid frontal assaults and defensive stands to establish the siege of Angband.
\end{itemize}

\entry{Founder}{Minas Tirith}{Tol Sirion, Beleriand}{F.A. 1 - F.A. 455}
\begin{itemize}[left=0.25\linewidth, noitemsep, before=\small]
    \footnotesize
    \item Established the fortress of Minas Tirith upon Tol Sirion.
    \item Demonstrated effective strategic planning and defensive capabilities.
\end{itemize}


\entry{Founder and Leader}{Nargothrond}{Nargothrond, Beleriand}{F.A. 52 - F.A. 465}
\begin{itemize}[left=0.25\linewidth, noitemsep, before=\small]
    \footnotesize
    \item Established and defended the underground fortress of Nargothrond.
    \item Skilled in underground engineering and architecture, earning the nickname "Felagund" (Hewer of Caves) from the Dwarves.
    \item Demonstrated strong leadership and strategic skills in guarding against the forces of Morgoth.
\end{itemize}

\entry{Ambassador to Men}{House of Bëor}{Estolad, Beleriand}{F.A. 116}
\begin{itemize}[left=0.25\linewidth, noitemsep, before=\small]
    \footnotesize
    \item Fostered strong relations with the newly arrived Men.
    \item Demonstrated exceptional skills in diplomacy and communication.
\end{itemize}

\entry{General, Soldier}{Dagor Bragollach}{Northern Beleriand}{F.A. 455}
\begin{itemize}[left=0.25\linewidth, noitemsep, before=\small]
    \footnotesize
    \item Led fierce but unsuccessful counter-offensives when the siege of Angband was first broken, and a disciplined fighting retreat against Morgoth's forces during the Battle of Sudden Flame.
    \item Strategically isolated during the battle, I was rescued from certain death by Barahir and his men, marking the beginning of a strong alliance with Men.
\end{itemize}

\entry{Expedition Lead}{Quest for the Silmaril}{Angband}{F.A. 465}
\begin{itemize}[left=0.25\linewidth, noitemsep, before=\small]
    \footnotesize
    \item Assisted Beren in his quest to recover a Silmaril from Morgoth's crown.
    \item Engaged Sauron in a battle of songs of power, demonstrating unyielding determination.
    \item When captured and imprisoned, I fought a werewolf in single combat using my bare hands and teeth. I succumbed to my injuries, but ensured Beren's survival.
\end{itemize}


\sectiontitle{Education}

\entry{Adept of Warfare}{Military Council of Maedhros}{Himring, Beleriand}{F.A. 10 - F.A. 50}
\begin{itemize}[left=0.25\linewidth, noitemsep, before=\small]
    \footnotesize
    \item Underwent intensive training in war strategy, tactics, and leadership under Maedhros, one of the foremost military minds of the Noldor.
\end{itemize}

% Skills
\sectiontitle{Interests}
\begin{itemize}[left=0.25\linewidth, noitemsep]
    \footnotesize
    \item Quenya, Sindarin, Khuzdul, Common Speech (Westron), Black Speech, Valarin.
    \item Adept at music (vocals and harp), communication, and enchantment.
\end{itemize}

\end{document}
